\PaperTitle

### 2019-12-11 paper/ec_submission/filter_bubble_ec.tex
Trying to work on ec formating

\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false}
\usepackage[T1]{fontenc}
%\usepackage{lmodern}
\usepackage{float}
\usepackage{enumitem}
\newtheorem{finding}{Finding}
%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2020}
\acmYear{2020}
\setcopyright{acmlicensed}
\acmConference[WWW'20]{Recomme '18: ACM Symposium on Neural Gaze Detection}{April 20-24, 2020}{Taipai, Taiwan}
\acmBooktitle{RecSys '19: ACM Conference on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
% end of the preamble, start of the body of the document source.

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{A User-Centric Approach to the Design and Consequences of Recommender Systems}
%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.

\settopmatter{printacmref=false} % Removes citation information below abstract
\makeatletter
\def\-copyrightspace{\relax}
\makeatother

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
We study a model of user decision-making in the context of recommender systems. We explore the extent to which two issues traditionally associated with recommender systems -- \textit{filter bubbles} and \textit{user homogenization} -- can be attributed to recommendation systems. The key component of our model is that users face a decision problem under uncertainty and that there are informational spillovers where a user consuming a product and learning how she values it reduces uncertainty about similar products. We find that this generates behavior consistent with filter bubble effects -- where users consume increasingly similar items over time -- and that recommendation can help alleviate these effects, as has been found in the empirical work of Nguyen et al. (2014). However, we find that recommendation, while alleviating filter bubble effects, leads to an increase in user homogeneity.
\par
We discuss the evaluation of recommender systems in light of these findings. Traditional design approaches to recommender systems only optimize for predicting user preferences after uncertainty has been resolved and ignore user beliefs and the inferences that users themselves make after consuming items. We propose an alternative interpretation of the serendipity measure where good recommendations are those that provide useful information, that is, information without which choice would be different and lead to worse outcomes on average relative to the case where no recommendation is provided. As a result, we emphasize the importance of understanding user behavior without recommendation, both for designing recommendations and understanding their impacts and usefulness.
\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\author{Guy Aridor}
\affiliation{
  \institution{Columbia University \\ Department of Economics}}

\author{Duarte Gon\c{c}alves}
\affiliation{%
  \institution{Columbia University, BRU-IL \\ Department of Economics}}

  \author{Shan Sikdar}
  \affiliation{Independent Researcher}
%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
%\keywords{Recommender Systems, Filter Bubbles, Serendipity}

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.

@@

\section{Introduction}

@@

Recommender systems have been influential in shaping consumer choice in these markets with 75\% of movies watched on Netflix and 35\% of page-views on Amazon coming from recommendations.\footnote{MacKenzie et al. (2013, Oct.),  How retailers can keep up with consumers. \url{https://www.mckinsey.com/industries/retail/our-insights/how-retailers-can-keep-up-with-consumers}. Retrieved on October 3, 2019.} While there are many positive effects from these systems, there is an increasing worry that there are unintended side-effects of recommendation systems. There have been claims that YouTube's recommendation algorithm unintentionally lead to the radicalization of many individuals,\footnote{Friedersdorf (2018, Mar. 12), YouTube Extremism and the Long Tail, \textit{The Atlantic}. \url{https://www.theatlantic.com/politics/archive/2018/03/youtube-extremism-and-the-long-tail/555350}. Retrieved on October 3, 2019.} that personalized recommender systems lead users into \textit{filter bubbles} where they effectively get isolated from a diversity of viewpoints or content \cite{pariser2011filter}, and that personalized recommender systems may also lead users to become increasingly homogenized at the same time \cite{chaney2018algorithmic, hosanagar2013will}.
\par

@@

The key components of our model are:
\begin{enumerate}[label=(\arabic*)]
\item Users face uncertainty about their valuation of the different goods and thus face a decision problem under under uncertainty.
\item Choice sets are large and users only consume a small fraction of this choice set over their lifetime.
\item Consumption of these items is sequential and users live for multiple periods.
\item Consuming an item provides information about the value of similar items in the product space.
\item Recommendation provides users with information, reducing their uncertainty.
\end{enumerate}

@@

\section{Our Model and Preliminaries}

\subsection{Preliminaries on Expected Utility Theory}
\noindent For every product $n$ in the product space $\mathcal J=\{0,1,....,N-1\}$, we assume that each consumer $i$ assigns a monetary equivalent $x_{i,n} \in \mathbb R$ to the experience of consuming it. Each consumer can value the same product in differently. However, we assume that users have the same utility over money, given by a utility function $u: \mathbb R \to \mathbb R$, strictly increasing and continuous. So, ex-post, the value of product $n$ for consumer $i$ is given by $u(x_{i,n})$ However, before consuming the product, the consumer does not know exactly how she will value it. In particular, even users that will end up having the same ex-post valuation of product $n$ may differ in their ex-ante valuation because they hold different beliefs about it. We denote by $p_{i}$ the beliefs consumer $i$ has about how she will value each of the products in the product space. Note that this implies that consuming product $n$ is the same as taking a gamble. Each individual evaluates the product according to the associated expected utility associated with the product, i.e. $U_i(n)=\mathbb E_{p_i}[u(x_n)]$. 
\par

@@

We denote by $x_{i,n}$ individual $i$'s realized value from consuming item $n$. In particular, we consider that the realized value derived from a given item can be decomposed in the following manner: $x_{i,n}= v_{i,n} + \beta v_n$, where $v_{i,n}$ denotes an idiosyncratic component -- i.e. user $i$'s idiosyncratic taste for product $n$ --  and $v_{n}$, a common-value component. One can interpret $v_n$ as a measure of how much product $n$ is valued in society in general and, in a sense, $v_{i,n}$ denotes how $i$ diverges from this overall ranking. The scalar $\beta \in \mathbb{R}_{t}$ denotes the degree to which valuations are idiosyncratic to each individual or common across individuals. If $\beta=0$, it is impossible to generate meaningful predictions of any one's individual preferences based on others, while if $\beta$ is large, every individual has similar preferences.
\par
Stacking values in vector-form, we get the vector of values associated with each item 
$${\left(x_{i,n}\right)}_{n \in \mathcal{J}}=:X_i =V_i+ \beta V $$
where $V_i ={\left(v_{i,n}\right)}_{n \in \mathcal{J}}$ and $V={\left(v_{n}\right)}_{n \in \mathcal{J}}$.
\par
\noindent\textbf{User Decision-Making.}
We assume the user makes $T$ choices and therefore can only consume up to $T$ items, where $T$ is but a small fraction of $N$. This captures the idea that users are faced with an immense choice set but that ultimately they end up experiencing (and learning) about just a small fraction of it. Since this is a sequential decision-making problem under uncertainty, in principle users face an exploration-exploitation trade-off. However, for tractability, we impose that users are myopic and every period consume the product that they have not yet tried ($n_i^t$) that gives them the highest expected utility given the information from past consumption offers ($C_i^{t-1}=(n_i^1,...,n_i^{t-1})$) and their initial beliefs.
\par
\noindent \textbf{User Beliefs.} We assume that users do not know the realized utilities of the goods before consuming an item.
Formally, consumer $i$ starts with some beliefs about $X_i$, namely that the idiosyncratic and common-value parts of the valuations are independent -- $V_i \perp \!\!\! \perp V$ -- and that each is multivariate normal 
\begin{enumerate}[topsep=0pt]
\item $V_i \sim \mathcal N (\overline V_i, \Sigma_i)$ 
\item $V \sim \mathcal N(\overline V, \Sigma)$ with $\overline V =0$
\end{enumerate}
We impose the normality assumption for two reasons. The first is that users update their beliefs using Bayesian updating and recall that the normal distribution forms a conjugate family, which allows for simple posterior updates. The second is that it allows us to incorporate an easily interpretable correlation structure between the items.
\par
Keeping with the assumption that $V_i$ represents idiosyncratic deviations from $V$, we assume that, on the population level, prior beliefs $\overline V_i=\left(\overline v_{i,n}\right)_{n \in \mathcal{J}}$ are drawn independently from a jointly normal distribution, where $\overline v_{i,n} \sim \mathcal N (0, \overline \sigma^2)$ are independent and identically distributed. These $\overline v_{i,n}$ denote the prior belief that individual $i$ holds about the her valuation over good $n$. As people are exposed to different backgrounds, their beliefs about what is good for them also varies and $\overline v_{i,n}$ denotes this idiosyncrasy at the level of prior beliefs.
\par

@@

In order to have a well-defined notion of similarity we need to define a distance function between goods, which we define as $d(n,m):=\min\{ \lvert m - n \rvert ,N - \lvert m - n \rvert \}$ where $m$ and $n$ are indices of items in $\mathcal{J}$. This distance function is not intended to model the intricacies of a realistic product space, but instead to provide a stylized product space to help us understand the effects of informational spillovers on user behavior. We consider that the entry of $n$-th row and the ($m$)-th column of $\Sigma_i$ is given by $\sigma_i^2 \rho^{d(n,m)}$, and that of $\Sigma$ is given by $\sigma^2 \rho^{d(n,m)}$. The scalar $\rho \in [0,1]$ therefore impacts the covariance structure: a higher $\rho$ implies that learning the utility of $n$ is more informative about products nearby. Informativeness, for any $\rho \in (0,1)$, is decreasing in distance. The particular distance function that we utilize leads to this covariance structure being simple, where the $(n,n+1)$-th entry in the covariance matrix is $\rho$, the $(n,n+2)$-th entry is $\rho^2$, etc.
\par
\begin{figure}[t]
\includegraphics[width=.4\linewidth]{Example-Bubbles.pdf}
\captionof{figure}{Illustrative Example}
\label{fig:illustrative_example}
\end{figure}

@@

We simulate over risk-aversion parameters $\gamma \in \{ 0, 0.3, 0.6, 1, 5 \}$, standard-deviation $\sigma \in \{ 0.25, 0.5, 1.0, 2.0, 4.0 \}$, correlation parameters $\rho\in \{ 0, 0.1, 0.3, 0.5, 0.7, 0.9 \} $ and degree of idiosyncrasy of individual valuations $\beta \in \{ 0, 0.4, 0.8, 1, 2, 5\}$. When we consider results varying a single parameter, we group the results over the other parameters and provide reports varying only the parameter of interest. We report results for a relatively small consumption history $T=20$ with a produce space size $N=200$. Unless otherwise reported, our results are robust to varying $N$.

@@

\begin{figure}[t]
\includegraphics[width=.9\linewidth]{figures/rho_pos_consumption_dist_N_200T_20_overall.pdf}\\
\includegraphics[width=.9\linewidth]{figures/rho_zero_consumption_dist_N_200T_20_overall.pdf}\\
\caption{Consumption path with (Top) and without (Bottom) correlation between values}
\label{fig:correlation_consumption_path}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{figures/rho_consumption_dist_N_200T_20.pdf}\\
\includegraphics[width=\linewidth]{figures/rho_consumption_dist_N_200T_20_partial.pdf}\\
\includegraphics[width=\linewidth]{figures/rho_consumption_dist_N_200T_20_omni.pdf}\\
\caption{Extent of Local Consumption for No Recommendation (Top), Recommendation (Middle) and Oracle (Bottom) for different Correlation values}
\label{fig:local_consumption_across_rho}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\linewidth]{figures/gamma_consumption_dist_N_200T_20.pdf}\\
\includegraphics[width=\linewidth]{figures/gamma_consumption_dist_N_200T_20_partial.pdf}\\
\includegraphics[width=\linewidth]{figures/gamma_consumption_dist_N_200T_20_omni.pdf}\\
\caption{Effect of Risk Aversion on Local Consumption for No Recommendation (Top), Recommendation (Middle) and Oracle (Bottom)}
\label{fig:no_rec_risk_aversion}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=.9\linewidth]{figures/gamma_diversity_N_200_T_20}
\captionof{figure}{Risk Aversion and Diversity}\label{fig:risk_aversion_diversity}
\end{figure}

\begin{finding}\label{finding_welfare_gap}
The welfare gap between the no recommendation and the recommendation regimes and that between the no recommendation and the oracle regimes are decreasing in $\rho$.
\end{finding}
However, interestingly, the decrease in diversity is \textit{not} associated with a decline in welfare. In fact, welfare stays roughly the same in the oracle and recommendation cases. The welfare gap between the no recommendation case and the other two cases \textit{decreases} as the diversity gap increases.
\par
\begin{figure}[t]
\includegraphics[width=.9\linewidth]{figures/rho_diversity_N_200_T_20.pdf}\\
\includegraphics[width=.9\linewidth]{figures/rho_welfare_N_200_T_20.pdf}\\
\captionof{figure}{Welfare, Diversity, and Correlation}\label{fig:diversity_correlation}
\end{figure}

@@

%\begin{figure}

%\end{figure}

This only happens since $\gamma = 0$ leads to users only caring about the expected value of the product. However, as we saw in Findings \ref{finding_local_consumption} and \ref{finding_diversity}, increasing $\gamma$ can lead to lower diversity and increasingly local consumption due to the fact that the degree of uncertainty now impacts users' choices. This weakens the negative relationship between diversity and welfare since both negative and positive experiences with a good reduce uncertainty about surrounding goods. This leads to the inverted-U shape found in Figure \ref{fig:diversity_welfare_ra} when $\gamma$ is relatively large (e.g $\gamma = 5$) though diversity and welfare are virtually uncorrelated in the data. In the recommendation and oracle regimes, under risk neutrality ($\gamma=0$), welfare and diversity and uncorrelated, while under risk aversion ($\gamma=5$), it is possible to observe in Figure \ref{fig:diversity_welfare_ra_partial} an actual positive relation between diversity and welfare as recommendations are able to reduce uncertainty and facilitate exploration of the product space.
\par
\begin{figure}[t]
\includegraphics[width=1.05\linewidth]{figures/diversity_welfare_rn.pdf}\\
\includegraphics[width=1.05\linewidth]{figures/diversity_welfare_ra.pdf}\\
\captionof{figure}{Diversity vs. Welfare, No-Recommendation, $\gamma = 0$ (Top), Diversity vs. Welfare, $\gamma = 5$ (Bottom)}\label{fig:diversity_welfare_ra}
\end{figure}
\begin{figure}[t]
\includegraphics[width=1.05\linewidth]{figures/diversity_welfare_rn_partial.pdf}\\
\includegraphics[width=1.05\linewidth]{figures/diversity_welfare_ra_partial.pdf}\\
\captionof{figure}{Diversity vs. Welfare, Recommendation, $\gamma = 0$ (Top), Diversity vs. Welfare, $\gamma = 5$ (Bottom)}\label{fig:diversity_welfare_ra_partial}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=.8\linewidth]{figures/beta_homogeneity_N_200_T_20}
\captionof{figure}{Strength of Recommendation and Homogeneity}\label{fig:beta_homo}
\end{figure}
~

\begin{figure}[t]
\includegraphics[width=.8\linewidth]{figures/rho_homogeneity_N_200_T_20}
\captionof{figure}{Correlation and Homogeneity}\label{fig:cor_homo}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{refs}
\end{document}

>>>>

\documentclass[format=acmsmall, review=false]{acmart}
\usepackage{acm-ec-20}
\usepackage{booktabs} % For formal tables
\usepackage[ruled]{algorithm2e} % For algorithms

\usepackage{subcaption}

\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Choose a citation style by commenting/uncommenting the appropriate line:
%\setcitestyle{authoryear}
\setcitestyle{acmnumeric}

\newtheorem{finding}{Finding}

% Title. Note the optional short title for running heads. In the interest of anonymization, please do not include any acknowledgements.
\newcommand\PaperTitle{A User-Centric Approach to the Design and Consequences of Recommender Systems}
\title[\PaperTitle]{\PaperTitle}

% Anonymized submission.
\author{Submission 42?}

% Abstract. Note that this must come before \maketitle.
\begin{abstract}
We study a model of user decision-making in the context of recommender systems. We explore the extent to which two issues traditionally associated with recommender systems -- \textit{filter bubbles} and \textit{user homogenization} -- can be attributed to recommendation systems. The key component of our model is that users face a decision problem under uncertainty and that there are informational spillovers where a user consuming a product and learning how she values it reduces uncertainty about similar products. We find that this generates behavior consistent with filter bubble effects -- where users consume increasingly similar items over time -- and that recommendation can help alleviate these effects, as has been found in the empirical work of Nguyen et al. (2014). However, we find that recommendation, while alleviating filter bubble effects, leads to an increase in user homogeneity.
\par
We discuss the evaluation of recommender systems in light of these findings. Traditional design approaches to recommender systems only optimize for predicting user preferences after uncertainty has been resolved and ignore user beliefs and the inferences that users themselves make after consuming items. We propose an alternative interpretation of the serendipity measure where good recommendations are those that provide useful information, that is, information without which choice would be different and lead to worse outcomes on average relative to the case where no recommendation is provided. As a result, we emphasize the importance of understanding user behavior without recommendation, both for designing recommendations and understanding their impacts and usefulness.
\end{abstract}

\begin{document}

@@

% Paper body
\section{Introduction}

@@

Recommender systems have been influential in shaping consumer choice in these markets with 75\% of movies watched on Netflix and 35\% 
of page-views on Amazon coming from recommendations.
\footnote{MacKenzie et al. (2013, Oct.),  How retailers can keep up with consumers. 
\url{https://www.mckinsey.com/industries/retail/our-insights/how-retailers-can-keep-up-with-consumers}. 
Retrieved on October 3, 2019.} 
While there are many positive effects from these systems, there is an increasing worry that there are unintended side-effects of recommendation systems. 
There have been claims that YouTube's recommendation algorithm unintentionally lead to the radicalization of many individuals,
\footnote{Friedersdorf (2018, Mar. 12), YouTube Extremism and the Long Tail, 
\textit{The Atlantic}. 
\url{https://www.theatlantic.com/politics/archive/2018/03/youtube-extremism-and-the-long-tail/555350}. Retrieved on October 3, 2019.} 
that personalized recommender systems lead users into \textit{filter bubbles} 
where they effectively get isolated from a diversity of viewpoints or content 
\cite{pariser2011filter}, and that personalized recommender systems may also 
lead users to become increasingly homogenized at the same time \cite{chaney2018algorithmic, hosanagar2013will}.
\par

@@

The key components of our model are:
\begin{enumerate}
\item Users face uncertainty about their valuation of the different goods and thus face a decision problem under under uncertainty.
\item Choice sets are large and users only consume a small fraction of this choice set over their lifetime.
\item Consumption of these items is sequential and users live for multiple periods.
\item Consuming an item provides information about the value of similar items in the product space.
\item Recommendation provides users with information, reducing their uncertainty.
\end{enumerate}

@@

\section{Our Model and Preliminaries}
\subsection{Preliminaries on Expected Utility Theory}
\noindent For every product $n$ in the product space $\mathcal J=\{0,1,....,N-1\}$, we assume that each consumer $i$ assigns a monetary equivalent $x_{i,n} \in \mathbb R$ to the experience of consuming it. Each consumer can value the same product in differently. However, we assume that users have the same utility over money, given by a utility function $u: \mathbb R \to \mathbb R$, strictly increasing and continuous. So, ex-post, the value of product $n$ for consumer $i$ is given by $u(x_{i,n})$ However, before consuming the product, the consumer does not know exactly how she will value it. In particular, even users that will end up having the same ex-post valuation of product $n$ may differ in their ex-ante valuation because they hold different beliefs about it. We denote by $p_{i}$ the beliefs consumer $i$ has about how she will value each of the products in the product space. Note that this implies that consuming product $n$ is the same as taking a gamble. Each individual evaluates the product according to the associated expected utility associated with the product, i.e. $U_i(n)=\mathbb E_{p_i}[u(x_n)]$. 
\par

@@

We denote by $x_{i,n}$ individual $i$'s realized value from consuming item $n$. In particular, we consider that the realized value derived from a given item can be decomposed in the following manner: $x_{i,n}= v_{i,n} + \beta v_n$, where $v_{i,n}$ denotes an idiosyncratic component -- i.e. user $i$'s idiosyncratic taste for product $n$ --  and $v_{n}$, a common-value component. One can interpret $v_n$ as a measure of how much product $n$ is valued in society in general and, in a sense, $v_{i,n}$ denotes how $i$ diverges from this overall ranking. The scalar $\beta \in \mathbb{R}_{t}$ denotes the degree to which valuations are idiosyncratic to each individual or common across individuals. If $\beta=0$, it is impossible to generate meaningful predictions of any one's individual preferences based on others, while if $\beta$ is large, every individual has similar preferences.
\par
Stacking values in vector-form, we get the vector of values associated with each item 
$${\left(x_{i,n}\right)}_{n \in \mathcal{J}}=:X_i =V_i+ \beta V $$
where $V_i ={\left(v_{i,n}\right)}_{n \in \mathcal{J}}$ and $V={\left(v_{n}\right)}_{n \in \mathcal{J}}$.
\par
\noindent\textbf{User Decision-Making.}
We assume the user makes $T$ choices and therefore can only consume up to $T$ items, where $T$ is but a small fraction of $N$. This captures the idea that users are faced with an immense choice set but that ultimately they end up experiencing (and learning) about just a small fraction of it. Since this is a sequential decision-making problem under uncertainty, in principle users face an exploration-exploitation trade-off. However, for tractability, we impose that users are myopic and every period consume the product that they have not yet tried ($n_i^t$) that gives them the highest expected utility given the information from past consumption offers ($C_i^{t-1}=(n_i^1,...,n_i^{t-1})$) and their initial beliefs.
\par
\noindent \textbf{User Beliefs.} We assume that users do not know the realized utilities of the goods before consuming an item.
Formally, consumer $i$ starts with some beliefs about $X_i$, namely that the idiosyncratic and common-value parts of the valuations are independent -- $V_i \perp \!\!\! \perp V$ -- and that each is multivariate normal 
\begin{enumerate}
\item $V_i \sim \mathcal N (\overline V_i, \Sigma_i)$ 
\item $V \sim \mathcal N(\overline V, \Sigma)$ with $\overline V =0$
\end{enumerate}
We impose the normality assumption for two reasons. The first is that users update their beliefs using Bayesian updating and recall that the normal distribution forms a conjugate family, which allows for simple posterior updates. The second is that it allows us to incorporate an easily interpretable correlation structure between the items.
\par
Keeping with the assumption that $V_i$ represents idiosyncratic deviations from $V$, we assume that, on the population level, prior beliefs $\overline V_i=\left(\overline v_{i,n}\right)_{n \in \mathcal{J}}$ are drawn independently from a jointly normal distribution, where $\overline v_{i,n} \sim \mathcal N (0, \overline \sigma^2)$ are independent and identically distributed. These $\overline v_{i,n}$ denote the prior belief that individual $i$ holds about the her valuation over good $n$. As people are exposed to different backgrounds, their beliefs about what is good for them also varies and $\overline v_{i,n}$ denotes this idiosyncrasy at the level of prior beliefs.
\par

@@

In order to have a well-defined notion of similarity we need to define a distance function between goods, which we define as $d(n,m):=\min\{ \lvert m - n \rvert ,N - \lvert m - n \rvert \}$ where $m$ and $n$ are indices of items in $\mathcal{J}$. This distance function is not intended to model the intricacies of a realistic product space, but instead to provide a stylized product space to help us understand the effects of informational spillovers on user behavior. We consider that the entry of $n$-th row and the ($m$)-th column of $\Sigma_i$ is given by $\sigma_i^2 \rho^{d(n,m)}$, and that of $\Sigma$ is given by $\sigma^2 \rho^{d(n,m)}$. The scalar $\rho \in [0,1]$ therefore impacts the covariance structure: a higher $\rho$ implies that learning the utility of $n$ is more informative about products nearby. Informativeness, for any $\rho \in (0,1)$, is decreasing in distance. The particular distance function that we utilize leads to this covariance structure being simple, where the $(n,n+1)$-th entry in the covariance matrix is $\rho$, the $(n,n+2)$-th entry is $\rho^2$, etc.
\par
\begin{figure}[t]
\includegraphics[width=.4\linewidth]{../Example-Bubbles.pdf}
\captionof{figure}{Illustrative Example}
\label{fig:illustrative_example}
\end{figure}

@@

We simulate over risk-aversion parameters $\gamma \in \{ 0, 0.3, 0.6, 1, 5 \}$, \ standard-deviation $\sigma \in \{ 0.25, 0.5, 1.0, 2.0, 4.0 \}$, correlation parameters $\rho\in \{ 0, 0.1, 0.3, 0.5, 0.7, 0.9 \} $ and degree of idiosyncrasy of individual valuations $\beta \in \{ 0, 0.4, 0.8, 1, 2, 5\}$. When we consider results varying a single parameter, we group the results over the other parameters and provide reports varying only the parameter of interest. We report results for a relatively small consumption history $T=20$ with a produce space size $N=200$. Unless otherwise reported, our results are robust to varying $N$.

@@

% \begin{figure}[t]
% \includegraphics[width=.9\linewidth]{../figures/rho_pos_consumption_dist_N_200T_20_overall.pdf}\\
% \includegraphics[width=.9\linewidth]{../figures/rho_zero_consumption_dist_N_200T_20_overall.pdf}\\
% \caption{Consumption path with (Top) and without (Bottom) correlation between values}
% \label{fig:correlation_consumption_path}
% \end{figure}

\begin{figure}
\begin{subfigure}{.5\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/rho_pos_consumption_dist_N_200T_20_overall.pdf}
  \caption{1a}
  \label{fig:sfig1}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{../figures/rho_zero_consumption_dist_N_200T_20_overall.pdf}
  \caption{1b}
  \label{fig:sfig2}
\end{subfigure}
\caption{Consumption path with (Top) and without (Bottom) correlation between values}
\label{fig:correlation_consumption_path}
\end{figure}

@@

% \begin{figure}[t]
% \includegraphics[width=\linewidth]{../figures/rho_consumption_dist_N_200T_20.pdf}\\
% \includegraphics[width=\linewidth]{../figures/rho_consumption_dist_N_200T_20_partial.pdf}\\
% \includegraphics[width=\linewidth]{../figures/rho_consumption_dist_N_200T_20_omni.pdf}\\
% \caption{Extent of Local Consumption for No Recommendation (Top), Recommendation (Middle) and Oracle (Bottom) for different Correlation values}
% \label{fig:local_consumption_across_rho}
% \end{figure}

\begin{figure}[t]
\begin{subfigure}{.5\textwidth}
\includegraphics[width=\linewidth]{../figures/rho_consumption_dist_N_200T_20.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\textwidth}
\includegraphics[width=\linewidth]{../figures/rho_consumption_dist_N_200T_20_partial.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\textwidth}
\includegraphics[width=\linewidth]{../figures/rho_consumption_dist_N_200T_20_omni.pdf}\\
\caption{Extent of Local Consumption for No Recommendation (Top), Recommendation (Middle) and Oracle (Bottom) for different Correlation values}
\end{subfigure}%
\label{fig:local_consumption_across_rho}
\end{figure}

\begin{figure}[t]
\begin{subfigure}{.5\textwidth}
\includegraphics[width=\linewidth]{../figures/gamma_consumption_dist_N_200T_20.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\textwidth}
\includegraphics[width=\linewidth]{../figures/gamma_consumption_dist_N_200T_20_partial.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\textwidth}
\includegraphics[width=\linewidth]{../figures/gamma_consumption_dist_N_200T_20_omni.pdf}\\
\end{subfigure}%
\caption{Effect of Risk Aversion on Local Consumption for No Recommendation (Top), Recommendation (Middle) and Oracle (Bottom)}
\label{fig:no_rec_risk_aversion}
\end{figure}

@@

\begin{figure}[ht]
\includegraphics[width=.4\linewidth]{../figures/gamma_diversity_N_200_T_20}
\captionof{figure}{Risk Aversion and Diversity}\label{fig:risk_aversion_diversity}
\end{figure}

\begin{finding}\label{finding_welfare_gap}
The welfare gap between the no recommendation and the recommendation regimes and that between the no recommendation and the oracle regimes are decreasing in $\rho$.
\end{finding}
However, interestingly, the decrease in diversity is \textit{not} associated with a decline in welfare. In fact, welfare stays roughly the same in the oracle and recommendation cases. The welfare gap between the no recommendation case and the other two cases \textit{decreases} as the diversity gap increases.
\par

% \begin{figure}[t]
% \includegraphics[width=.9\linewidth]{../figures/rho_diversity_N_200_T_20.pdf}\\
% \includegraphics[width=.9\linewidth]{../figures/rho_welfare_N_200_T_20.pdf}\\
% \captionof{figure}{Welfare, Diversity, and Correlation}\label{fig:diversity_correlation}
% \end{figure}

\begin{figure}
\begin{subfigure}{.5\linewidth}
  \includegraphics[width=.8\linewidth]{../figures/rho_diversity_N_200_T_20.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
  \includegraphics[width=.8\linewidth]{../figures/rho_welfare_N_200_T_20.pdf}
\end{subfigure}
\captionof{figure}{Welfare, Diversity, and Correlation}\label{fig:diversity_correlation}
\end{figure}

@@

This only happens since $\gamma = 0$ leads to users only caring about the expected value of the product. However, as we saw in Findings \ref{finding_local_consumption} and \ref{finding_diversity}, increasing $\gamma$ can lead to lower diversity and increasingly local consumption due to the fact that the degree of uncertainty now impacts users' choices. This weakens the negative relationship between diversity and welfare since both negative and positive experiences with a good reduce uncertainty about surrounding goods. This leads to the inverted-U shape found in Figure \ref{fig:diversity_welfare_ra} when $\gamma$ is relatively large (e.g $\gamma = 5$) though diversity and welfare are virtually uncorrelated in the data. In the recommendation and oracle regimes, under risk neutrality ($\gamma=0$), welfare and diversity and uncorrelated, while under risk aversion ($\gamma=5$), it is possible to observe in Figure \ref{fig:diversity_welfare_ra_partial} an actual positive relation between diversity and welfare as recommendations are able to reduce uncertainty and facilitate exploration of the product space.
\par
\begin{figure}[t]
\begin{subfigure}{.5\textwidth}
\includegraphics[width=1.05\linewidth]{../figures/diversity_welfare_rn.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\textwidth}
\includegraphics[width=1.05\linewidth]{../figures/diversity_welfare_ra.pdf}
\end{subfigure}\\
\captionof{figure}{Diversity vs. Welfare, No-Recommendation, $\gamma = 0$ (Top), Diversity vs. Welfare, $\gamma = 5$ (Bottom)}\label{fig:diversity_welfare_ra}
\end{figure}

\begin{figure}[t]
\begin{subfigure}{.5\textwidth}
\includegraphics[width=1.05\linewidth]{../figures/diversity_welfare_rn_partial.pdf}
\end{subfigure}\\
\begin{subfigure}{.5\textwidth}
\includegraphics[width=1.05\linewidth]{../figures/diversity_welfare_ra_partial.pdf}
\end{subfigure}\\
\captionof{figure}{Diversity vs. Welfare, Recommendation, $\gamma = 0$ (Top), Diversity vs. Welfare, $\gamma = 5$ (Bottom)}\label{fig:diversity_welfare_ra_partial}
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=.4\linewidth]{../figures/beta_homogeneity_N_200_T_20}
\captionof{figure}{Strength of Recommendation and Homogeneity}\label{fig:beta_homo}
\end{figure}
~

\begin{figure}[t]
\includegraphics[width=.4\linewidth]{../figures/rho_homogeneity_N_200_T_20}
\captionof{figure}{Correlation and Homogeneity}\label{fig:cor_homo}
\end{figure}

@@

% Start of "Sample References" section
% In the interest of anonymization, please do not include acknowledgements in your submission.
%
%\begin{acks}
%
%	The authors would like to thank Dr. Maura Turolla of Telecom
%	Italia for providing specifications about the application scenario.
%
%	The work is supported by the \grantsponsor{GS501100001809}{National
%		Natural Science Foundation of
%		China}{http://dx.doi.org/10.13039/501100001809} under Grant
%	No.:~\grantnum{GS501100001809}{61273304\_a}
%	and~\grantnum[http://www.nnsf.cn/youngscientsts]{GS501100001809}{Young
%		Scientsts' Support Program}.
%
%
%\end{acks}

% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{../refs}

\end{document}
